\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry} % Page margins
\usepackage{hyperref} % For links
\usepackage{enumitem} % For customizing lists
\usepackage{titlesec} % For section formatting
\usepackage{color} % For colored text

\definecolor{darkblue}{RGB}{0,0,120}

\titleformat{\section}{\Large\bfseries\color{darkblue}}{\thesection}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}


\titleformat{\subsection}{\large\bfseries}{\thesubsection}{0em}{}
\titlespacing{\subsection}{0pt}{6pt}{2pt}

\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kishor Pokharel}}\\
    \vspace{0.25em}
    \href{mailto:kishorpokharel7@gmail.com}{kishorpokharel7@gmail.com}$\bullet$
    \href{https://www.linkedin.com/in/kishor-pokharel-7192951b0}{LinkedIn}$\bullet$
    Biratnagar, Nepal
\end{center}


\section*{About Me}
Experienced software developer with expertise in web development, backend services, database design.

\section*{Education}
\subsection*{Birat Multiple College (Tribhuvan University)}
\textbf{Bachelor in Computer Science and IT} \hfill \textit{2019-2024}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Relevant Coursework: Data Structures, Algorithms, Database Systems, Web Development
\end{itemize}

\section*{Work Experience}

\subsection*{Software Developer | Crowdinvest} \hfill \textit{October 2023 - September 2024}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built a customizable static website using HubSpot modules for dynamic content configuration.
    \item Worked on building CrowdInvest platform using React, Nodejs, Postgres.
    \item Worked on CrowdInvest Mobile App using React Native.
\end{itemize}

\subsection*{Backend Developer | Diliflow} \hfill \textit{Jan 2025 - Present}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built a zero-cost, serverless proof of concept of the Diliflow platform using Cloudflare Workers.
    \item Built workflow automation APIs for dynamic, configurable due-diligence processes on the platform.
    \item Implemented a Retrieval-Augmented Generation (RAG) system to extract and analyze documents.
\end{itemize}

\section*{Skillset}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Programming Languages:} Golang, Typescript, JavaScript
    \item \textbf{Technologies:} SQL, Node.js, HTML/CSS, React, React Native
    \item \textbf{Databases:} PostgreSQL, SQLite, Mysql
    \item \textbf{Tools:} Linux, Git, Cloudflare Workers, Docker
\end{itemize}

\section*{Personal Projects}

\subsection*{Chat App}
\begin{itemize}[leftmargin=*, noitemsep]
    \item A concurrent real-time chat application with user authentication and global chat room.
    \item Technology used: Golang, Websockets, Postgresql, Javascript, Html, Css
    \item \href{https://github.com/KishorPokharel/go-chatapp}{https://github.com/KishorPokharel/go-chatapp}
\end{itemize}

\subsection*{Kanban Board Api}
\begin{itemize}[leftmargin=*, noitemsep]
    \item A backend for Kanban board application allowing users to add tasks, update task stages, and reorder tasks based on priority within each stage.
    \item Technology used: Golang, Postgresql
    \item \href{https://github.com/KishorPokharel/kanban}{https://github.com/KishorPokharel/kanban}
\end{itemize}

\subsection*{2D Snake Game}
\begin{itemize}[leftmargin=*, noitemsep]
    \item The classic snake game with go and sdl2.
    \item Technology used: Golang, SDL2
    \item \href{https://github.com/KishorPokharel/snek}{https://github.com/KishorPokharel/snek}
\end{itemize}

\subsection*{Gamehub}
\begin{itemize}[leftmargin=*, noitemsep]
    \item A website to discover games using rawg api.
    \item Technology used: React, Typescript, Chakra UI
    \item \href{https://gamehub-nine.vercel.app}{https://gamehub-nine.vercel.app}
\end{itemize}

\end{document}
